---
title: "Graphic Description for SDD Curse"
description: |
  A graphic description about urchins.
catégorie :
  - Data Sciences I
author:
  - name: Raphaël Deroux
    url: {}
  - name: Nicolas Devilez
    url: {}
  - name: Engels Guyliann
    url: https://guyliann.netlify.com/fr
date: 11-15-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# package
SciViews::R
options(data.io_lang = "fr")
```

## Data Import

```{r importation}

urchin <- read("urchin_bio", package = "data.io")
```

The urchin dataset is a set of data collected from a total of 421 urchins. It presents essentially  measurements and mass surveys. There are also categories according to sex and origin.

## Graphic


```{r}

chart(urchin, skeleton ~ weight %col=% origin | origin) +
  geom_point(na.rm = TRUE) +
  labs(x = "Total weight", y = "Skeleton's mass")
```

It's easy to see that urchins raised on farms are obviously slightly larger than those found in the wild. This is probably due to a selection process in favor of a larger mass of urchins.
